### 2018-08-01 doc/plos/text/manuscript.tex
commentary on accuracy vs sensors

\subsection*{Accuracy relative to data sources}

The error (measured in MAE and RMSE) of nowcasts of ILI for the US as a whole
relative to the same error for each data source are shown in
Fig~\ref{figure_accuracy_vs_sensors}.

@@

\subsection*{Accuracy relative to baselines}

@@

>>>>

\subsubsection*{Accuracy relative to data sources}

For the US as a whole, Fig~\ref{figure_accuracy_vs_sensors} compares error
(measured in MAE and RMSE) between nowcasts and individual data sources. To
control for the fact that difficulty varies over time, the evaluation is
performed only over weeks on which the nowcast and the particular data source
are jointly available. The number of weeks in each such union is indicated in
each corresponding subpanel.

@@

In all instances, the nowcast has lower error (both MAE and RMSE) than any
individual data source, subject to the fitting procedure described above. This
indicates, at least for the US as a whole, that the nowcast is on average more
accurate than any individual data source.

\subsubsection*{Accuracy relative to baselines}

@@

That the nowcast is more accurate than its individual inputs should hold in
general as the outputs of sensor fusion should, on average, have smaller error
than the inputs. However, this may not hold in all cases due to overfitting or
violations of the assumptions of linearity and normality.
